Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-05 manuscript-chicago.Rmd
Final version (pre-redaction)

Thus, lexical and interpersonal cohesion are hypothesized to be tied to social
and political cohesion. Shared language in an online environment may lead to the
development or expression of a shared identity [@wiltermuth2009synchrony]. This,
in turn, may drive individuals' propensity to engage in similar coordinated
behavior on behalf of the group [@wiltermuth2009synchrony; @walton2012mere].
Taken together, these two processes may increase movement participants' weak and
strong ties [@granovetter1977strength; @gladwell2010revolution;
@mcadam1986recruitment], strengthening the movement overall by expanding and
deepening heterogenous ties. Therefore, in the context of social conflict, the
linguistic cohesion of the online conversation should correspond to the degree
of social cohesion on the ground.

Steinert-Threlkeld [-@steinert2017spontaneous] modeled a similar relationship
between social media and social mobilization alongside event data. That
groundbreaking work demonstrated that participants on the fringe of a social
movement contribute substantially to the overall level of protest. In addition
to providing new methods to this growing field of study, we build on this
previous work by demonstrating how sociolinguistic cohesion evolves in
tandem with negative and positive exogenous events.

@@

Sociolinguistic cohesion is not a static concept. Just as social movements
experience increased participation and setbacks---indicating dynamic
relationships among participants and between participants and the sociopolitical
environment---sociolinguistic cohesion is also dynamic, reflecting the changing
states of the political sphere. Other scholars have noted the diffusion of
messages whereby they reach a critical mass, allowing for “behaviors, beliefs, and
preferences” to spread within a population [@barash2012critical]. Cohesion
changes over time in response to external events and the internal dynamics of
the social movement, even if the social interaction occurs entirely 
online [@centola2007complex].

Lexical cohesion, then, is a useful indicator of social cohesion in
political crisis. Lexical cohesion happens at the word level. Interlocutor
cohesion happens between speakers. Political cohesion happens at the social
level during moments of political crisis, like civil wars and social movements.
Sociolinguistic cohesion is comprised of lexical, interlocutor, and
socio-political events, where the words and their context reveal the disposition
of socially connected linguistic communities. It accounts for the cohesion between
multiple speakers in an environment whose language evolves to become more
aligned and similar. Sociolinguistic cohesion also addresses how groups involved
in political rebellion must have internal cohesion to overcome the collective
action problem to mount sustained resistance to state authority.

@@

## Data Preparation
### Social Cohesion Metric
The social cohesion or linguistic similarity of daily tweets was calculated by
quantifying the frequency of shared content words with respect to those words'
frequencies in the entire tweet corpus. If a linguistic term has a high
frequency in one tweet but has a low frequency in the whole tweet corpus, then
it is more likely a content word and is thus given more weight in calculating
social cohesion. This method is similar to inverse document frequency (IDF). For
more information on IDF, see @jones1972statistical and
@robertson2004understanding.

>>>>

Thus, lexical and interpersonal cohesion are hypothesized to be tied to social
and political cohesion. Shared online language may lead to the development or
expression of shared identity [@wiltermuth2009synchrony]. This, in turn, may
drive individuals' propensity to engage in coordinated behavior for the group
[@wiltermuth2009synchrony; @walton2012mere]. Taken together, these processes may
increase movement participants' weak and strong ties [@granovetter1977strength;
@gladwell2010revolution;
@mcadam1986recruitment], building the movement by expanding and deepening
heterogenous ties. Therefore, during social conflict, the linguistic cohesion
of the online conversation should correspond to the degree of social cohesion on
the ground.

Steinert-Threlkeld [-@steinert2017spontaneous] modeled a similar relationship
between social media and social mobilization alongside event data. That
groundbreaking work demonstrated that participants on the fringe of a social
movement contribute substantially to the overall level of protest. Here, in
addition to providing new methods to this area, we build on this work by
demonstrating how sociolinguistic cohesion evolves in tandem with negative and
positive exogenous events.

@@

Sociolinguistic cohesion is not a static concept. Just as social movements
experience increased participation and setbacks---indicating dynamic
relationships among participants and between participants and the sociopolitical
environment---sociolinguistic cohesion is also dynamic, reflecting the changing
states of the political sphere. Other scholars have noted the diffusion of
messages that reach critical mass, allowing for “behaviors, beliefs, and
preferences” to spread within a population [@barash2012critical]. Cohesion
changes over time in response to external events and the internal dynamics of
the social movement, even if the social interaction occurs entirely 
online [@centola2007complex].

Lexical cohesion, then, is a useful indicator of social cohesion in political
crisis. Lexical cohesion happens at the word level. Interlocutor cohesion
happens between speakers. Political cohesion happens at the social level during
moments of political crisis, like civil wars and social movements.
Sociolinguistic cohesion comprises lexical, interlocutor, and sociopolitical
events, in which the words and their context reveal the disposition of socially
connected linguistic communities. It accounts for the cohesion between multiple
speakers in an environment as their language becomes more similar.
Sociolinguistic cohesion also addresses how groups involved in political
rebellion converge to mount sustained resistance to state authority.

@@

## Data Preparation
### Social Cohesion Metric
The social cohesion or linguistic similarity of daily tweets was calculated by
quantifying the frequency of shared content words with respect to those words'
frequencies in the entire tweet corpus. If a linguistic term has a high
frequency in one tweet but has a low frequency in the whole tweet corpus, then
it is more likely a content word and is thus given more weight in calculating
social cohesion. This method is similar to *term frequency-inverse document
frequency* [tf-idf; see also @jones1972statistical;
@robertson2004understanding].
